\documentclass[12pt]{article}
\usepackage{fullpage,times}

%\pagestyle{empty}



\begin{document}


\begin{center}

{\Large 
{\it Diamond Trust of London}

Quick Start Guide
}

Jason Rohrer

December 15, 2009

\end{center}


\paragraph{Game goal}

At the end of 8 rounds, the player with the most diamonds wins.  In the event of a tie in the diamond count, the player with the most money wins.

\paragraph{Game overview}
Each player commands three diamond-trading {\bf agents}.  Your agents start out in your {\bf home region}, which is the green area in the upper left of the map.  Each player starts out with 2 diamonds and \$18.

The main action in the game involves flying your agents into and around Angola to buy the diamonds that are being produced there.

\paragraph{Buying Diamonds}
When you send an agent into a region of Angola, you must decide how much you're willing to pay for the diamonds that have accumulated in that region.  Here's how this works:
\begin{itemize}
\item Both player pay the amount that they specify, regardless of who wins.
\item The player who pays the most in a region gets all of the diamonds there.
\item If no one pays in a regions, the diamonds stay there.
\item In the event of a tie in a region, the diamonds stay there.
\end{itemize}
Agents carry the diamonds that they buy until they return to their home region.

\paragraph{UN Inspector}
The Inspector blocks diamond sales in her region and confiscates any agent-held diamonds.  The inspector can be moved with a bribe.  The same rules for diamond buying apply to inspector bribes (both players pay, the highest payer gets to move the Inspector).

\paragraph{Agent travel costs}
Flying around costs money.  Within Angola, flights between regions cost \$1, but flying between Angola and your home region (across the ocean) costs \$2.

\paragraph{Selling diamonds}
Diamonds that your agents bring back to your home region can be sold to bring in extra money.  You get to pick how many to sell each round.  If you sell 0, you get a base income of \$18.  If you sell some, you may get as much as \$24, but it depends on how many your opponent sells.  You and your opponent split \$24 based on your fraction of the total number sold.

\paragraph{Agent loyalty}
Along with paying for diamonds, you also can pay salaries to your agents and pay bribes to your opponent's agents.  An agent is loyal to whoever has paid it the most, total, so far.  Some notes:
\begin{itemize}
\item To pay one of your agents salary, that agent must be in your home region.
\item To bribe an opponent's agent, one of your agents must share a region with that opponent agent.
\end{itemize}
If one of your agents is loyal to you, it will protect your secrets (such as its own salary, its destination, your money balance).  If your opponent bribes one of your agents, she will be able to see this secret info, and vice verse if you bribe an opponent's agent.

\paragraph{Putting it all together}
The game is played in 8 rounds.  During a round, you and your opponent go through the following phases, in this order:
\begin{enumerate}
\item Pay salaries/bribes.
\item Move agents, specify diamond payments in agent destinations, and specify Inspector bribes.
\item Move the Inspector (if necessary).
\item Highest payers collect diamonds.
\item Sell diamonds and gain income
\end{enumerate}
In each phase, you and your opponent make your decisions simultaneously, in secret.




\end{document}
